Eurovision Song Contest: semifinal 1, 2009

### 2021-02-23 inst/eurovision.Rmd
typos

The file `eurovision.txt`, defined below, is copied from "Eurovision
Song Contest 2009," Wikipedia, accessed May 13, 2018.  It refers to
semi-final 1.  More documentation is given in `eurovision.Rd` [type
`help(euro2009)` at the `R` prompt].

@@

'''{r,label=equalptesteurovision,cache=TRUE}
equalp.test(eurovision)
```

>>>>

The file `eurovision.txt`, used below, is copied from "Eurovision Song
Contest 2009," Wikipedia, accessed May 13, 2018.  It refers to
semi-final 1.  More documentation is given in `eurovision.Rd` [type
`help(euro2009)` at the `R` prompt].

@@

```{r,label=equalptesteurovision,cache=TRUE}
equalp.test(eurovision)
```
